---
title: "Trading Analysis"
output: word_document
date: "2024-03-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Install the RGP package 

```{r}
install.packages("Packages/rgp_0.4-1.tar.gz", repos = NULL, type = "source")

# run `install.packages('emoa')` the rerun this cell 
```

**Load the required data and libraries**

```{r}
# Load the relevant libraries
library(tidyverse)
library(quantmod)
library(TTR)
library(ggplot2)
library(rgp)
library(rgenoud)
library(mlr)
```

The libraries are loaded. The data was then imported

```{r}
# Load the required data
df <- read_csv("stocks-data.csv", show_col_types = FALSE)
```

# Explanatory Data Analysis 
## Data Assessment
What are the first five records of the dataset

```{r}
head(df)
```

How is the dataset structured?

```{r}
dim(df)
```

Are there any null values in the dataset? 

```{r}
sum(is.na(df))
```

There are no null values in the dataset 

Lets check some duplicated rows 

```{r}
sum(duplicated(df))
```

There are no duplicated row 


# Trading Rules

Create some dummy features that will define the trading rule

```{r}
df$SMA_20 <- SMA(df$Close, n=20)
df$SMA_50 <- SMA(df$Close, n=50)
df$RSI <- RSI(df$Close)
```

The trading rule is simple, buying is done when SMA_20 is greater than SMA_50

```{r}
trading_rule <- expression(SMA_20 > SMA_50)
trading_rule
```

Now lets define the fitness function

```{r}
fitness_fun <- function(y) {
  # Get the required features from the stock data
  new_data <- data.frame(SMA_50 = df$SMA_50,
                         SMA_20 = df$SMA_20,
                         fitness = ifelse(eval(trading_rule), 1, -1))
  
  # Thereafter the fitness is calculated for instance cumulative returns 
  new_data$returns <- c(0, diff(new_data$Close))
  fitness <- sum(new_data$returns * new_data$fitness)
  return(fitness)
}
```


then define the search space 

```{r}
#search_space <- list(
#  SMA_50 = runif(1, min = min(df$SMA_50), max = max(df$SMA_50)),
#  SMA_20 = runif(1, min = min(df$SMA_20), max = max(df$SMA_20))
#)

min_value1 = min(df$SMA_20)
max_value1 = max(df$SMA_20)
min_value2 = min(df$SMA_50)
max_value2 = max(df$SMA_50)

search_space <- list(
  c(min_value1, max_value1),  # Domain for variable 1
  c(min_value2, max_value2)  # Domain for variable 2
  # Add more variables as needed
)
```

Run the Genetic programming 

```{r}
#GP <- genoud(fitness_fun, domains = search_space, maxit = 100)
task <- makeSymbolicRegressionTask(df$Close, df$RSI)
result <- gp(task, fitness_fun)
print(result$bestIndividual)
```


