---
title: "Trading-Analysis-revised"
output: word_document
date: "2024-03-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Install the RGP package 

```{r}
install.packages("Packages/rgp_0.4-1.tar.gz", repos = NULL, type = "source")

# run `install.packages('emoa')` the rerun this cell 
```

**Load the required data and libraries**

```{r}
# Load the relevant libraries
library(tidyverse)
#library(quantmod)
library(TTR)
#library(ggplot2)
#library(rgp)
#library(rgenoud)
#library(mlr)
```


```{r}
# Load the required data
df <- read_csv("stocks-data.csv", show_col_types = FALSE)
```

# Explanatory Data Analysis 
## Data Assessment
What are the first five records of the dataset

```{r}
head(df)
```


How is the dataset structured?

```{r}
dim(df)
```

Are there any null values in the dataset? 

```{r}
sum(is.na(df))
```

There are no null values in the dataset 

Lets check some duplicated rows 

```{r}
sum(duplicated(df))
```

```{r}
library(dygraphs)
```

## Data Visualization

```{r}

plot(x=df$Date, y=df$Close)
```

```{r}
#dygraph(df$Close, main = "GOOGLE Stock Price") %>%
#  dyRangeSelector(dateWindow = c("2013-12-18", "2016-12-30"))

# Subset the data frame to include only date and Close price
close_data <- df[, c("Date", "Close")]

# Plot the chart using dygraph
dygraph(close_data, main = "Close Price Over Time")

```


# Trading Rules 
Define the trading rule here 

```{r}
# Calcuate a 20 day and 50 day moving average 
df$SMA_20 <- SMA(df$Close, 20)
df$SMA_50 <- SMA(df$Close, 50)
```

```{r}
dygraph(df[,c('SMA_20','SMA_50', "Date")],main = 'GOOG Moving Averages') %>%
  dySeries('SMA_50', label = 'SMA_50') %>%
  dySeries('SMA_50', label = 'SMA_50') %>%
  dyRangeSelector(height = 30) %>%
  dyShading(from = '2016-4-28', to = '2016-7-27', color = '#CCEBD6') %>%
  dyShading(from = '2016-7-28', to = '2016-12-30', color = '#FFE6E6')
```

# PAUSE HERE 


```{r}
# Load the quantmod library
library(quantmod)

# Assuming you have a data frame df with columns "date", "Close", "SMA_50", and "SMA_20"

# Create a column for the trading signal
df$signal <- NA

# Generate buy signals when SMA_20 crosses above SMA_50
df$signal[df$SMA_20 > df$SMA_50 & lag(df$SMA_20) <= lag(df$SMA_50)] <- "buy"

# Generate sell signals when SMA_50 is greater than SMA_20
df$signal[df$SMA_50 > df$SMA_20 & lag(df$SMA_50) <= lag(df$SMA_20)] <- "sell"

# Plot Close prices with buy and sell signals
chart_Series(df$Close, name = "Close Price", theme = "white")
add_SMA(n = 20, col = "blue")
add_SMA(n = 50, col = "red")
add_TA(df$signal, type = "p", col = "green", on = 1)

```


```{r}
# Load necessary libraries
library(quantmod)
library(rgp)  # For Genetic Programming
library(rgenoud)

# Define fitness function for GP
fitness_function <- function(rule) {
  # Execute trading rule
  signals <- eval(rule)
  
  # Extract signals
  signals <- signals[nrow(signals), ]
  
  # Calculate returns based on signals
  returns <- Return.calculate(df$Close, subset = signals)
  
  # Fitness function (e.g., maximize Sharpe ratio)
  return(SharpeRatio.annualized(returns))
}

# Define search space for GP
search_space <- expression(
  ifelse(SMA_20 > SMA_50, 1, 0)
)

# Set up and run GP
GP <- genoud(fitness_function, nvars=1, max = TRUE, pop.size = 3000) # domains = list(rule = search_space), maxit = 100)

# Extract best trading rule
best_rule <- GP$par

# Evaluate best rule
best_signals <- eval(best_rule)

# Plot signals
chart_Series(your_stock_symbol, name = "Stock Price")
add_SMA(n = 20, col = "blue")
add_SMA(n = 50, col = "red")
add_TA(best_signals, type = "p", col = "green", on = 1)
```

```{r}
# Load necessary libraries
library(quantmod)
library(PerformanceAnalytics) # For Sharpe Ratio calculations 
library(rgp)  # For Genetic Programming

# Example data.frame with Close and Date columns
rownames(df) <- df$Date #Convert date column to index

# Calculate SMA_20 and SMA_50
df$SMA_20 <- SMA(df$Close, n = 20)
df$SMA_50 <- SMA(df$Close, n = 50)

# Define fitness function for GP
fitness_function <- function(rule) {
  # Execute trading rule
  signals <- eval(rule)
  
  # Calculate returns based on signals
  returns <- xts(diff(df$Close * signals))
  
  # Fitness function (e.g., maximize Sharpe ratio)
  return(SharpeRatio.annualized(returns))
}

# Define search space for GP
search_space <- expression(
  ifelse(SMA_20 > SMA_50, 1, 0)
)

# Set up and run GP
GP <- genoud(fitness_function, Domains = list(rule = search_space), nvars = 1)

# Extract best trading rule
best_rule <- GP$par

# Evaluate best rule
best_signals <- eval(best_rule)

# Plot signals
chart_Series(df$Close, name = "Stock Price")
add_SMA(n = 20, col = "blue")
add_SMA(n = 50, col = "red")
add_TA(best_signals, type = "p", col = "green", on = 1)
```

The project was terminated

